Generating Simulated Data

### 2021-03-23 docs/SimData.Rmd
more dummy data fleet effort

# dimensions for singletons file
singletons <- data.frame(
  debug=3,
  Nyrs=NOBAom_ms$runpar$nyears, #may want to take from survey time series instead
  Nspecies=length(sppsubset$Name),
  Nsizebins=5,
  Nareas=1,
  Nfleets=5,
  Nsurveys=2,
  wtconv=1,
  yr1Nphase=0,
  recphase=0,
  avg_rec_phase=0,
  avg_F_phase=0,
  dev_rec_phase=0,
  dev_F_phase=0,
  fqphase=0,
  sqphase=0,
  ssig_phase=0,
  csig_phase=0,
  phimax=1,
  scaleInitialN=1,
  otherFood=0000,
  LFI_size=60,
  bandwidth_metric=5,
  assessmentPeriod=3,
  flagMSE=0,
  flagLinearRamp=1,
  baseline_threshold=0.2
)

# M1 same for all species, depends on n length bins
M1mat <- matrix(0.02, singletons$Nspecies, singletons$Nsizebins, 
                dimnames = list(c(sort.default(sppsubset$Name)),  c(paste0("sizeclass",seq(1:singletons$Nsizebins))))) 
M1 <- as.data.frame(M1mat)

@@

@@

# write the csvs
o.name <- here("simulated-data/msinput/hydra/")
write_csv(foodweb, paste0(o.name,"foodweb_NOBA.csv"))
write_csv(specieslist, paste0(o.name,"speciesList_NOBA.csv"))
write_csv(lenwtpar, paste0(o.name,"lengthweight_species_NOBA.csv"))
write.csv(intakespp, paste0(o.name,"intake_species_NOBA.csv"))
write.csv(sizepref, paste0(o.name,"mortality_M2sizePreference_NOBA.csv"))
write.table(t(singletons), paste0(o.name,"singletons_NOBA.csv"), sep=",",  col.names=FALSE)
write.csv(M1, paste0(o.name,"mortality_M1_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"recruitment_covariates_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"maturity_covariates_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"growth_covariates_NOBA.csv"))

>>>>

# dimensions for singletons file
singletons <- data.frame(
  debug=3,
  Nyrs=NOBAom_ms$runpar$nyears, #may want to take from survey time series instead
  Nspecies=length(sppsubset$Name),
  Nsizebins=5,
  Nareas=1,
  Nfleets=length(unique(NOBAom_ms$truecatchage_ss$fleet)),
  Nsurveys=2,
  wtconv=1,
  yr1Nphase=0,
  recphase=0,
  avg_rec_phase=0,
  avg_F_phase=0,
  dev_rec_phase=0,
  dev_F_phase=0,
  fqphase=0,
  sqphase=0,
  ssig_phase=0,
  csig_phase=0,
  phimax=1,
  scaleInitialN=1,
  otherFood=0000,
  LFI_size=60,
  bandwidth_metric=5,
  assessmentPeriod=3,
  flagMSE=0,
  flagLinearRamp=1,
  baseline_threshold=0.2
)

# M1 same for all species, depends on n length bins
# to get annual M1 of 0.1, this matrix needs to be M1 per timestep
# right now input works for 5 timesteps per year, but should be 
# done in the code with input annual M1 in case timestep changes
M1mat <- matrix(0.02, singletons$Nspecies, singletons$Nsizebins, 
                dimnames = list(c(sort.default(sppsubset$Name)),  c(paste0("sizeclass",seq(1:singletons$Nsizebins))))) 
M1 <- as.data.frame(M1mat)

# sexratio fixed 50:50 for all species
# sexratio <- vector(0.5, )
# rbind(species = sort.default(sppsubset$Name),
#                   ratio = rep(0.5))
# colnames(sexratio) <- sexratio[1,]
# sexratio <- as.data.frame(sexratio[-1,])

@@

# placeholder for effort data dimensioned by year and nfleets
allfleets <- atlantisom::load_fisheries(d.name, fisheries.file)
fleets <- unique(NOBAom_ms$truecatchage_ss$fleet)

dummyeffort <- data.frame(1:singletons$Nyrs,
                          matrix(1, singletons$Nyrs, singletons$Nfleets))
names(dummyeffort) <- c("year", fleets)

@@

# write the csvs
o.name <- here("simulated-data/msinput/hydra/")
write_csv(foodweb, paste0(o.name,"foodweb_NOBA.csv"))
write_csv(specieslist, paste0(o.name,"speciesList_NOBA.csv"))
write_csv(lenwtpar, paste0(o.name,"lengthweight_species_NOBA.csv"))
write.csv(intakespp, paste0(o.name,"intake_species_NOBA.csv"))
write.csv(sizepref, paste0(o.name,"mortality_M2sizePreference_NOBA.csv"))
write.table(t(singletons), paste0(o.name,"singletons_NOBA.csv"), sep=",",  col.names=FALSE)
write.csv(M1, paste0(o.name,"mortality_M1_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"recruitment_covariates_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"maturity_covariates_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"growth_covariates_NOBA.csv"))
write_csv(dummyeffort, paste0(o.name,"observation_effort_NOBA.csv"))
